---
title: "Direct benevolence manipulation analysis"
author: "Matt Jaquiery (matt.jaquiery@psy.ox.ac.uk)"
output:
  html_notebook:
    toc: yes
    toc_depth: 3
    css: ../src/writeUp.css
    includes:
      after_body: ../src/toc_menu.html
  html_document:
    df_print: paged
    toc: yes
    toc_depth: '3'
    css: ../src/writeUp.css
    includes:
      after_body: ../src/toc_menu.html
editor_options:
  chunk_output_type: inline
---

July 2019

[Script run `r Sys.time()`]


```{r prematter, include = F}

library(testthat)

library(tidyverse)

library(BayesFactor)
library(BayesMed)

library(prettyMD)

library(knitr)

opts_chunk$set('echo' = F)

set.seed(20190723)

# Plot setup
theme_set(theme_light() + 
            theme(panel.grid.major.x = element_blank()))

```

```{r loadData, include = F}

studyVersion <- "1-3-0"
studyName <- "directBenevolence"

overrideMarkerList <- c(11) # Someone managed to get marker width 8 for one question, not sure how

exclude <- list(
  maxAttnCheckFails = 0, # pass all attn checks
  maxTrialRT = 60000,    # trials take < 1 minute
  minTrials = 11,        # at least 11 trials completed
  minChangeRate = .1,    # some advice taken on 10%+ of trials
  multipleAttempts = T   # exclude multiple attempts
  ) 

skipLoadData <- F

source("src/02_Exclusions.R")

```

# Introduction

Observations from [evolutionary models](https://github.com/oxacclab/EvoEgoBias) show that egocentric discounting is a successful strategy in environments where advisors sometimes provide deliberately poor advice. We reason that human participants may show a sensitivity to these contextual factors underlying advice-taking and respond to them in a rational manner. To test the effects of potentially misleading advice, we used a direct benevolence manipulation to pair participant judges in a judge-advisor system with two advisors, one who they were told would consistently try to help them ('in-group advisor'), and one who they were told may occasionally try to mislead them ('out-group advisor').

We hypothesised that participants would place greater weight on the advice of the in-group vs out-group advisor, and that this relationship would be mediated by responses to questionnaires asking about the perceived benevolence of the advisor.

# Method

The experimental code is available on [GitHub](https://github.com/oxacclab/ExploringSocialMetacognition), and the experiement can be performed by visiting [https://acclab.psy.ox.ac.uk/~mj221/ESM/ACv2/db.html](https://acclab.psy.ox.ac.uk/~mj221/ESM/ACv2/db.html?PROLIFIC_PID=WriteUp). 

# Results

## Exclusions

```{r exclusions}

tmp <- suppressWarnings(left_join(exclusions, okayIds, by = "pid"))

tmp$condition <- factor(tmp$condition, labels = c("InFirst",
                                                  "OutFirst"))

table(tmp$excluded, tmp$condition)

```

Our final participant list consists of `r length(unique(PP$pid))` participants who completed an average of `r num2str(mean(aggregate(number ~ pid, PP, function(x) sum(x) / 2)$number))` trials each.

## Task performance

```{r bindAdvisors}

# bind feedback property from participants

# convert pid columns to character to allow joining
tmp <- PP
tmp$pid <- as.character(tmp$pid)

advisors$pid <- as.character(advisors$pid)

advisors <- advisors[advisors$pid %in% tmp$pid, ]
advisors <- left_join(advisors, unique(tmp[c("pid", "feedback")]), "pid")

# drop practice advisors
advisors <- advisors[advisors$idDescription != "Practice", ]

```

First we offer a characterisation of the task, to provide the reader with a sense of how the participants performed. 

### Decisions

Participants offered estimates of the year in which various events took place. The correct answers were always between 1900 and 2000, although the timeline on which participants responded went from 1890 to 2010 in order to allow extra room for advice. Participants answered by dragging a marker onto a timeline which covered a range of 11 years (e.g. 1940-1950). Participants were informed that a correct answer was one in which the marker covered the year in which the event took place.

#### Correctness

Responses are regarded as **correct** if the target year is included within the marker range.

```{r accuracy}

tmp <- markerBreakdown(responseCorrect, decisions, hideTotals = T)
tmp <- rbind(tmp$first, tmp$last)[, c(1, 3)]

num2str.tibble(tmp, isProportion = T, precision = 3)

```

```{r accuracyGraph}

ggplot(aggregate(responseCorrect ~ 
                   responseMarker + decision + pid,
                 decisions, mean), 
       aes(x = decision, y = responseCorrect)) +
  geom_violin(alpha = .25, colour = NA, fill = "grey75") +
  geom_boxplot(fill = NA, outlier.color = NA) +
  geom_line(alpha = .5, aes(colour = pid, group = pid)) + 
  geom_point(alpha = .5, aes(colour = pid)) +
  stat_summary(geom = "line", fun.y = mean,
               aes(group = 1, linetype = "mean"), size = 1.5) +
  scale_linetype_manual(values = c("dashed")) + 
  labs(x = "response marker width (years)", 
       y = "p(response correct)")

```

#### Error (estimate mean)

The **error** is calcualted as the distance from the centre of the answer marker to the correct year. It is thus possible for **correct** answers to have non-zero error, and it is likely that the error for correct answers scales with the marker size.

```{r err}

tmp <- markerBreakdown(responseError, decisions, hideTotals = T)
tmp <- rbind(tmp$first, tmp$last)[, c(1, 3)]

num2str.tibble(tmp, isProportion = T, precision = 3)

```

```{r errGraph}

ggplot(aggregate(responseError ~ 
                   responseMarker + decision + pid,
                 decisions, mean), 
       aes(x = decision, y = responseError)) +
  geom_violin(alpha = .25, colour = NA, fill = "grey75") +
  geom_boxplot(fill = NA, outlier.color = NA) +
  geom_line(alpha = .5, aes(colour = pid, group = pid)) + 
  geom_point(alpha = .5, aes(colour = pid)) +
  stat_summary(geom = "line", fun.y = mean,
               aes(group = 1, linetype = "mean"), size = 1.5) +
  scale_linetype_manual(values = c("dashed")) + 
  labs(x = "response marker width (years)", 
       y = "|target - response marker centre| (years)")

```

### Timing

We can look at the response time - the difference between the time the response is opened and the time the response is received.  

```{r time}

decisions$rt <- decisions$responseTimeEstimate - decisions$timeResponseOpen

tmp <- markerBreakdown(rt, decisions, hideTotals = T)
tmp <- rbind(tmp$first, tmp$last)[, c(1, 3)]

num2str.tibble(tmp, isProportion = T, precision = 3)

```

```{r timeGraph}

ggplot(aggregate(rt ~ 
                   responseMarker + decision + pid,
                 decisions, mean), 
       aes(x = decision, 
           y = rt / 1000)) +
  geom_violin(alpha = .25, colour = NA, fill = "grey75") +
  geom_boxplot(fill = NA, outlier.color = NA) +
  geom_line(alpha = .5, aes(colour = pid, group = pid)) + 
  geom_point(alpha = .5, aes(colour = pid)) +
  stat_summary(geom = "line", fun.y = mean,
               aes(group = 1, linetype = "mean"), size = 1.5) +
  scale_linetype_manual(values = c("dashed")) + 
  labs(x = "response marker width (years)", 
       y = "response time (s)")

```

### Summary {.summary}

Participants took longer on their final decisions, and slightly improved their accuracy. This suggests that they took the time to weigh up the advice, and that they took it into account when making their (final) decisions.

## Advisor performance

The advice offered should be equivalent between in/out group advisors.

### Accuracy

```{r adviceAccuracy}

tmp <- NULL
for (a in advisorNames) {
  eq <- as.formula(paste0("cbind(", a, ".accurate, ", 
                          a, ".error) ~ pid"))
  r <- aggregate(eq, AdvisedTrial, mean, na.rm = T)
  
  colnames(r) <- c("pid", "accuracy", "error")
  r$advisor = a
  
  tmp <- rbind(tmp, as.tibble(r))
}

prop2str(as.tibble(aggregate(cbind(accuracy, error) ~ advisor, 
                             tmp, 
                             mean, na.rm = T)), 
         precision = 3)

```

```{r adviceAccuracyGraph}

tmp <- gather(tmp, key = "var", value = "value", c("accuracy", "error"))

for (v in unique(tmp$var)) 
  print(
    ggplot(tmp[tmp$var == v, ], aes(x = advisor, y = value, colour = pid)) +
      geom_violin(colour = NA, fill = "grey75", alpha = .25) +
      geom_boxplot(outlier.colour = NA, fill = NA, aes(group = advisor)) +
      geom_line(alpha = .5, aes(colour = pid, group = pid)) + 
      geom_point(alpha = .5, aes(colour = pid)) +
      stat_summary(geom = "line", fun.y = mean,
                   aes(group = 1, linetype = "mean"), size = 1.5) +
      labs(y = v)
  )

```

### Agreement

```{r adviceAgreement}

tmp <- NULL
for (a in advisorNames) {
  eq <- as.formula(paste0(a, ".agree ~ pid"))
  r <- aggregate(eq, AdvisedTrial, mean, na.rm = T)
  
  colnames(r) <- c("pid", "agreement")
  r$advisor <- a
  tmp <- rbind(tmp, r)
}

prop2str(as.tibble(aggregate(agreement ~ advisor, 
                             tmp, mean, na.rm = T)), 
         precision = 3)

```

```{r adviceAgreementGraph}

ggplot(tmp, aes(x = advisor, y = agreement, colour = pid)) +
  geom_violin(colour = NA, fill = "grey75", alpha = .25) +
  geom_boxplot(outlier.colour = NA, fill = NA, aes(group = advisor)) +
  geom_line(alpha = .5, aes(colour = pid, group = pid)) + 
  geom_point(alpha = .5, aes(colour = pid)) +
  stat_summary(geom = "line", fun.y = mean,
               aes(group = 1, linetype = "mean"), size = 1.5)

```

### Distance

Distance is the continuous version of agreement - the difference between the centre of the advice and the centre of the initial estimate. 

```{r adviceDistance}

tmp <- NULL
for (a in advisorNames) {
  eq <- as.formula(paste0(a, ".distance ~ pid"))
  r <- aggregate(eq, AdvisedTrial, mean, na.rm = T)
  
  colnames(r) <- c("pid", "distance")
  r$advisor = a
  
  tmp <- rbind(tmp, as.tibble(r))
}

prop2str(as.tibble(aggregate(distance ~ advisor, 
                             tmp, 
                             mean, na.rm = T)), 
         precision = 3)

```

```{r adviceDistanceGraph}

ggplot(tmp, aes(x = advisor, y = distance, colour = pid)) +
  geom_violin(colour = NA, fill = "grey75", alpha = .25) +
  geom_boxplot(outlier.colour = NA, fill = NA, aes(group = advisor)) +
  geom_line(alpha = .5, aes(colour = pid, group = pid)) + 
  geom_point(alpha = .5, aes(colour = pid)) +
  stat_summary(geom = "line", fun.y = mean,
               aes(group = 1, linetype = "mean"), size = 1.5)

```

### Summary {.summary}

The advisors were similar in terms of their objective accuracy and their tendency to offer advice close to the participants' initial decisions. 

### Influence

The measure of influence is weight-on-advice. This is well-defined for values between 0 and 1 (trucated otherwise), and is
$$\text{WoA} = (\text{final} - \text{inital}) / (\text{advice} - \text{initial})$$
, or the degree to which the final decision moves towards the advised answer.

Influence is the primary outcome measure, and is thus expected to differ between advisors and feedback conditions.

```{r woa}

tmp <- NULL
for (a in advisorNames) {
  eq <- as.formula(paste0(a, ".woa ~ pid"))
  r <- aggregate(eq, AdvisedTrial, mean, na.rm = T)
  
  colnames(r) <- c("pid", "WoA")
  r$advisor <- a
  tmp <- rbind(tmp, r)
}

prop2str(as.tibble(aggregate(WoA ~ advisor, tmp, mean, na.rm = T)), 
         precision = 3)

```

```{r woaGraph}

ggplot(tmp, aes(x = advisor, y = WoA, colour = pid)) +
  geom_violin(colour = NA, fill = "grey75", alpha = .25) +
  geom_boxplot(outlier.colour = NA, fill = NA, aes(group = advisor)) +
  geom_line(alpha = .5, aes(colour = pid, group = pid)) + 
  geom_point(alpha = .5, aes(colour = pid)) +
  stat_summary(geom = "line", fun.y = mean,
               aes(group = 1, linetype = "mean"), size = 1.5) +
  scale_y_continuous(limits = c(0, 1))

```

##### WoA distribution

It's good to keep a general eye on the distribution of weight-on-advice on a trial-by-trial basis. 

```{r woaDistribution}

ggplot(AdvisedTrial, aes(woa)) + 
  geom_histogram(stat = "count") +
  facet_grid(feedback ~ advisor0idDescription, labeller = label_both)

```

### Summary {.summary}

Weight on Advice scores are highly similar identical between the advisors, as are the distributions. Participants tend to have different weight on advice for both advisors (shallow slopes), with mixed preferences (similar numbers have higher weight on advice for each advisor). This suggests that participants have preferences between advisors, but that these preferences are not systematically different between the advisors. Formal testing of the hypothesis is below.

## Questionnaire data

```{r questionnaires}

tmp <- debrief.advisors[debrief.advisors$pid %in% AdvisedTrial$pid, ]
tmp$sameGroup <- NA

for (i in seq(nrow(tmp))) {
  tmp$sameGroup[i] <- as.character(
    advisors$idDescription[advisors$pid == tmp$pid[i] &
                             advisors$id == tmp$advisorId[i]])
}

tmp <- gather(tmp, key = "Q", value = "rating", 
              c("knowledge", "helpfulness", "consistency", "trustworthiness"))

ggplot(tmp, aes(x = sameGroup, y = rating)) +
  geom_violin(colour = NA, fill = "grey75", alpha = .25) +
  geom_boxplot(outlier.colour = NA, fill = NA, aes(group = sameGroup)) +
  geom_line(alpha = .5, aes(colour = pid, group = pid)) + 
  geom_point(alpha = .5, aes(colour = pid)) +
  stat_summary(geom = "line", fun.y = mean,
               aes(group = 1, linetype = "mean"), size = 1.5) +
  scale_y_continuous(limits = c(0, 100)) +
  facet_wrap(. ~ Q, labeller = label_both)

```

### Summary {.summary} 

Across all questions there is no pronounced preference for the ingroup vs outgroup advisor, there does seem to be a difference in perceived consistency. The other measures, including 'trustworthiness' and 'helpfulness', show little difference. This is surpising because participants were explicitly informed that one advisor was more trustworthy and was trying to help more than the other. 

## Hypothesis testing

The hypotheses being tested here are:  

1. Participants will place higher weight on the advice of in-group advisors
  
2. Participants weighting of advisors by group will be mediated by reports of perceived advisor benevolence

### Group differences

Participants have different weight-on-advice for ingroup as opposed to outgroup advisors.

```{r h1, results='asis'}

tmp <- aggregate(inGroup.woa ~ pid, AdvisedTrial, mean, na.rm = T)
tmp$outGroup.woa <- 
  aggregate(outGroup.woa ~ pid, AdvisedTrial, mean, na.rm = T)$outGroup.woa

r <- md.ttestBF(tmp$inGroup.woa, tmp$outGroup.woa, 
              c("*M*|inGroup", "*M*|outGroup"), paired = T)
cat(r)

```

### Summary {.summary}

The Bayes factor indicates there is good evidence to support the claim that the participants do not place greater weight on the advice of one advisor versus the other.

### Mediation by benevolence

```{r h2, results='asis'}

tmp <- aggregate(advisor0woa ~ pid + advisor0idDescription + advisor0id, 
                 AdvisedTrial, mean, na.rm = T)
names(tmp) <- c("pid", "sameGroup", "id", "WoA")

for (i in seq(nrow(tmp))) {
  tmp$benevolence[i] <- debrief.advisors$helpfulness[
    debrief.advisors$pid %in% tmp$pid[i] &
      debrief.advisors$advisorId %in% tmp$id[i]
  ]
}

tmp$sameGroupDummy <- as.numeric(tmp$sameGroup == "inGroup")

r <- jzs_med(independent = tmp$sameGroupDummy, 
             dependent = tmp$WoA, 
             mediator = tmp$benevolence, 
             standardize = T)

r$main_result

plot(r$main_result)

```

### Summary {.summary}

These data support the conclusion that there are no meaningful associations between advisor group, subjective advisor assessment of benevolence ('helpfulness'), and the extent to which advice is taken.

## Exploration

Taking a look at the comments about what the difference between the advisors is (the participant are told explicitly), we can see whether it looks like there's an obvious break between participants for whom the manipulation was effective and those for whom it was not.

```{r commentBreakdown}

tmp <- aggregate(advisor0woa ~ pid + advisor0idDescription, AdvisedTrial, mean)
pids <- tibble(pid = unique(tmp$pid))
pids$worked <- sapply(unique(tmp$pid), function(pid) {
  x <- tmp[tmp$pid == pid, ]
  x$advisor0woa[x$advisor0idDescription == "inGroup"] > 
    x$advisor0woa[x$advisor0idDescription == "outGroup"]
})

pids <- pull(pids[pids$worked, ], "pid")

```

Participants for whom the manipulation worked: 

```{r commentManipSuccess}

kable(debrief.form$comment[debrief.form$pid %in% pids])

```

And those for whom it did not:

```{r commmentManipFail}

kable(debrief.form$comment[!(debrief.form$pid %in% pids)])

```

### Summary {.summary}

The comments appear to be fairly balanced between the participants for whom the manipulation worked, and those for whom it did not. If anything, the participants for whom the manipulation was unsuccessful provided more appropriate comments than those for whom it was successful.

# Conclusions

The experiment provided evidence against the hypotheses tested. Weight on advice was not higher for ingroup vs outgroup advisors, and the differences in the weighting of advice were not mediated by perceived benevolence. 

These results are odd. Participants told explicitly that one advisor is better should show a greater tendency to follow the advice of that advisor. It is perhaps possible that participants are attending more to the advice itself than the source of the advice. It is also possible that the high variation in advice makes it hard for participants to perform the task (although this variation was introduced due to non-effects in the previous minimal groups version of the manipulation). 

Another explanation, which may warrant empirical testing, is that participants respond to being warned about potentially misleading advice by selectively increasing their discounting of suspicious advice rather than by increasing discounting for all advice. 

## Recommendation {.summary}

This manipulation should work. It may be worth reducing the variation in advice (making the advisors better), and perhaps also allowing _actual_ differences in advice to follow the ostensible differences, to check whether the resistence to the manipulation is rational (because there are no differences in actual advice quality) or simply bullheaded (because participants don't care about the advisors). 

# Credits 

## Acknowledgements

Thanks as always to Nick Yeung and the other folks at the [ACC Lab](https://www.psy.ox.ac.uk/research/attention-cognitive-control-lab).

## R Packages

```{r results = 'asis'}
# list packages
packageNames <- (.packages())
# don't include very core package
packageNames <- packageNames[!(packageNames %in% 
                                 rownames(installed.packages(
                                   priority = "base")))]
# but do include the base package
packageNames <- c("base", packageNames)
out <- NULL
for (p in packageNames) {
  out <- rbind(out, data.frame('Package' = p, 
                               'Citations' = paste(format(citation(p), 
                                                          style = 'textVersion'), 
                                                   collapse = '<br/><br/>')))
}

kable(out)
```

## Funding

Matt Jaquiery is funded by a studentship from the [Medical Research Council](https://mrc.ukri.org/) (reference 1943590) and the University of Oxford [Department of Experimental Psychology](https://www.psy.ox.ac.uk/) (reference 17/18_MSD_661552).

## Technical details  

```{r results = 'hold'}
cat(paste('Time stamp:', Sys.time(), '\n\n'))
cat('Runtime \n')
proc.time()
cat('\n')
sessionInfo()
```