---
title: "Date estimation power analysis"
author: "Matt Jaquiery (matt.jaquiery@psy.ox.ac.uk)"
output:
  html_document:
    df_print: paged
    toc: yes
    toc_depth: '3'
  html_notebook:
    includes:
      after_body: ../src/toc_menu.html
    toc: yes
    toc_depth: 3
editor_options:
  chunk_output_type: inline
---

May 2019

[Script run `r Sys.time()`]

## Power Analysis

Pilots of the experimental design in versions 0.0.21-2 inidicated that the experiment was functioning sufficiently well to test the core claim that advisors' advice is processed differently according to the presence or absence of feedback (**feedback**) and the past advice profile of the advisor (**advisor**).

We have two estimates of the effect size, which we can use to ensure our pre-registered version is sufficiently powered. Power analysis will be conducted in [G*Power](http://www.gpower.hhu.de/). 

## G*Power

### Effect size f

Effect sizes observed in the previous versions:


version | effect size ($\eta^2$)  
:-------|:----------------------
0.0.21  | .173  
0.0.22  | .242  
mean    | .2075  


Our effect size estimates are in $\eta^2$, and they need to be in $f$. The [G*Power manual](http://www.gpower.hhu.de/fileadmin/redaktion/Fakultaeten/Mathematisch-Naturwissenschaftliche_Fakultaet/Psychologie/AAP/gpower/GPowerManual.pdf) helpfully informs us that $f = \sqrt{\eta^2 (1 - \eta^2)}$, so we'll put our mean $\eta^2$ through that process to get $f = .512$.

### Corr among rep measures

We need the correlation for the within-subject factor, so let's estimate that from the data in the versions in question:

```{r repObsCor}

library(tibble)
library(knitr)

# load data
version <- c("0-0-21", "0-0-22")

correlations <- tibble(version, cor = 0)

for (v in version) {
  
  s <- paste0("https://acclab.psy.ox.ac.uk/~mj221/ESM/data/public/", 
              "datesStudy_v", v, "_")
  
  okayIds <- as.tibble(read.csv(paste0(s, "metadata.csv")))
  
  okayIds$okay <- grepl("prolific", okayIds$tags)
  
  tmp <- as.tibble(read.csv(paste0(s, "AdvisedTrial.csv")))
  tmp <- tmp[tmp$pid %in% okayIds$pid[okayIds$okay], ]
  
  tmp$pid <- factor(tmp$pid)
  tmp$advisor0idDescription <- factor(tmp$advisor0idDescription)
  
  # calculate weight on advice
  i <- tmp[, "responseEstimateLeft"] + 
    (tmp[, "responseMarkerWidth"] - 1) / 2
  f <- tmp[, "responseEstimateLeftFinal"] + 
    (tmp[, "responseMarkerWidthFinal"] - 1) / 2
  adv <- tmp[, "advisor0advice"]
  
  x <- ((f - i) / (adv - i))
  
  x[x < 0] <- 0
  x[x > 1] <- 1
  
  tmp[, "woa"] <- x
  
  # aggregate by pid and advisor
  tmp <- aggregate(woa ~ advisor0idDescription + pid, tmp, mean)
  tmp <- tmp[order(tmp$pid), ]

  # correlate by pid
  correlations$cor[correlations$version == v] <- 
    cor(tmp$woa[tmp$advisor0idDescription == "Accurate"],
        tmp$woa[tmp$advisor0idDescription == "Agreeing"])

}

correlations

mean(correlations$cor)

```

### G*Power

[!G*power image](../img/dateEstimation_Power-analysis.png)

```
[1] -- Tuesday, May 28, 2019 -- 13:54:19
F tests - ANOVA: Repeated measures, within-between interaction
Analysis:	A priori: Compute required sample size 
Input:	Effect size f	=	.512
	α err prob	=	0.05
	Power (1-β err prob)	=	0.95
	Number of groups	=	4
	Number of measurements	=	2
	Corr among rep measures	=	0.558
	Nonsphericity correction ε	=	1
Output:	Noncentrality parameter λ	=	23.7234389
	Critical F	=	3.2388715
	Numerator df	=	3.0000000
	Denominator df	=	16.0000000
	Total sample size	=	20
	Actual power	=	0.9630315
```

## Conclusion

We require 20 participants (5 per cell) for 95% power. This is surprisingly reasonable!

## Credits 

### Acknowledgements

Thanks as always to Nick Yeung and the other folks at the [ACC Lab](https://www.psy.ox.ac.uk/research/attention-cognitive-control-lab).

### R Packages

```{r results = 'asis'}
# list packages
packageNames <- (.packages())
# don't include very core package
packageNames <- packageNames[!(packageNames %in% 
                                 rownames(installed.packages(
                                   priority = "base")))]
# but do include the base package
packageNames <- c("base", packageNames)
out <- NULL
for (p in packageNames) {
  out <- rbind(out, data.frame('Package' = p, 
                               'Citations' = paste(format(citation(p), 
                                                          style = 'textVersion'), 
                                                   collapse = '<br/><br/>')))
}

kable(out)
```

### Funding

Matt Jaquiery is funded by a studentship from the [Medical Research Council](https://mrc.ukri.org/) (reference 1943590) and the University of Oxford [Department of Experimental Psychology](https://www.psy.ox.ac.uk/) (reference 17/18_MSD_661552).

### Technical details  

```{r results = 'hold'}
cat(paste('Time stamp:', Sys.time(), '\n\n'))
cat('Runtime \n')
proc.time()
cat('\n')
sessionInfo()
```