---
title: "sim-calibration-knowledge_power-analysis"
author: "Matt Jaquiery"
date: "25/02/2020"
output: html_document
---

```{r echo = F, include = F}
library(tidyverse)
library(ggpubr)
library(broom)
library(BayesFactor)
library(prettyMD)
library(knitr)
library(parallel)

opts_chunk$set('echo' = F)

set.seed(20191216)

# Plot setup
theme_set(theme_light() + 
            theme(panel.grid.major.x = element_blank()))

rDir <- "http://localhost/ExploringSocialMetacognition/data/public/"
testData <- T

studyVersion <- "0-0-8"
studyName <- "calibrationKnowledge"

exclude <- list(
  maxTrialRT = 60000,    # trials take < 1 minute
  minTrials = 11,        # at least 11 trials completed
  minChangeRate = .1     # some advice taken on 10%+ of trials
  ) 

skipLoadData <- F

source("src/02_Exclusions.R")

```

## Data 

Here's the data we'll be playing with. It's generated by multiple runs of our integration tests.

```{r}

AdvisedTrial

```

## Parameters

We need to set up some parameters to explore. For now we'll just use different levels of the effect size, but we specify some other stuff anyway.

```{r}

params <- tibble(
  agentInsensitivitySD = 8,
  agentConfidence = 2,
  agentConfidenceSD = 4,
  agentEgoBias = .7, 
  agentEgoBiasSD = .2,
  agentEffectSize = seq(.0, .2, by = .005),
  agentEffectSizeSD = .1
)

params <- crossing(tibble(nAgents = seq(10, 50, 10)), params)

params

```

## Simulations

Now we run the simulations with those parameters.

```{r}
source('src/sim-confidence-estimation.R')

sim <- powerAnalysis(AdvisedTrial, params, "simulateCK")
sim$models$analysis <- analyseCK(sim$models$data)

peek <- cbind(
  parameter = apply(sim$parameters, 1, 
                    function(x) paste0(x, collapse = ';')),
  sim$models$analysis
) %>%
  mutate(parameter = factor(parameter))

names(peek)[1] <- paste0(names(sim$parameters), collapse = ';')

peek

```

## Heatmap

A better way to look at this is probably a heatmap. For this we'll want a few repetitions at each parameter set. This may take a long time to run!

```{r}

paramReps <- crossing(tibble(reps = 1:20), params)

paramReps <- paramReps %>% select(-reps)

simReps <- powerAnalysis(AdvisedTrial, paramReps, "simulateCK")
simReps$models$analysis <- analyseCK(simReps$models$data)

peek <- simReps$models$analysis %>%
  cbind(simReps$parameters, .) %>%
  group_by_at(vars(names(simReps$parameters))) %>%
  summarise_all(~ mean(. < .05, na.rm = T)) %>%
  rename(failed = okay)

peek

```

To look at each of these effects with a heatmap we need to restore the old structure.

```{r}

peek <- peek %>%
  pivot_longer(cols = c(contains(':'))) %>%
  mutate(strategy = str_extract(name, '[a-zA-Z]+_'),
         name = str_replace(name, strategy, ''),
         strategy = gsub('_', '', strategy),
         strategy = factor(strategy)) %>%
  rename(`p(p < .05)` = value,
         `p(failed)` = failed)

peek

```

```{r fig.height=10, fig.width=10}

for (n in unique(peek$name)) {
  for (s in unique(peek$strategy)) {
    x <- peek %>% 
      filter(name == n, strategy == s)
    print(
      x %>% 
        mutate(p = sprintf('%-.1f', `p(p < .05)`)) %>%
        ggplot(aes(x = nAgents, y = agentEffectSize, fill = `p(p < .05)`)) +
        geom_tile() +
        geom_text(aes(label = p)) + 
        coord_fixed(max(x$nAgents) / max(x$agentEffectSize)) +
        scale_fill_viridis_c(limits = c(0, 1), option = 'plasma') +
        labs(caption = paste0('Effect = ', n, '; Strategy = ', s))
    )
  }
}

```

## Power curves

Nick's minimum effect size of interest approach is to select a priori the number of participants we're going to test and work out what effect size we'd be able to detect with some amount of power. So we can use a single sample size and draw power curves by underlying effect size. 

We start off by examining these with the data we have...

```{r}

peek %>%
  filter(nAgents == 30,
         strategy != 'LikelihoodWeighted') %>%
  ggplot(aes(x = agentEffectSize, y = `p(p < .05)`, colour = name,
             size = name == 'pid:hybrid')) +
  geom_hline(yintercept = .05, colour = 'grey', size = 1) +
  geom_hline(yintercept = .95, colour = 'black', linetype = 'dashed') +
  geom_line() +
  scale_size_manual(values = c(.5, 1)) +
  facet_wrap(~strategy) +
  theme(legend.position = 'top',
        panel.grid = element_blank()) +
  labs(caption = paste0('Power curves for n = 30, reps = 20. Effect size the same for advisor and hybrid effects.'))

```
