---
title: "agreement-effects analysis"
output: html_notebook
---

Here we run code which simulates agents who exhange advice with one another and update their weightings of one another based on the agreement of their initial decisions and advice.

We want to see whether confidence-weighted updating has more pronounced effects than non-weighted agreement-only updating.

```{r}

n <- list(p = 6, d = 200) # numbers of participants and decisions
conf <- T                 # whether to use confidence-weighted adivsor update
biasMean <- 1             # +/- mean for bias distributions
lambda <- .1              # learning rate
saveAnimation <- F        # whether to save an animation
  
source('agreement-effects.R')

```

```{r}

n <- list(p = 6, d = 200) # numbers of participants and decisions
conf <- F                 # whether to use confidence-weighted adivsor update
biasMean <- 1             # +/- mean for bias distributions
lambda <- .1              # learning rate
saveAnimation <- F        # whether to save an animation

source('agreement-effects.R')

```

The decisions invesitaged above are discrete. Because of this, agents do not update their expectations of future decisions (i.e. their bias) after making a decision. We can also investigate what happens when agents **bias**, as well as their **assessment of other agents** is able to change. Bias changes based on the final decision made by an agent according to Bayes' rule:

Posterior = Prior * Evidence

$$P(H1 | Data) = \frac{P(H1) * P(Data | H1)}{(P(Data|H1)P(H1)) + (P(Data|¬H1)P(¬H1))}$$

In this case $Data$ is 1 or 0, according to the direction of the final decision. $H1$ is that the outcome will be >0 every time. 