---
title: "Advisor Choice simulation"
output: html_notebook
---

```{r prematter, include = F}

library(tidyverse)

```

# Simulation by virtual agents 

## Agent definition  

Virtual agents differ parametrically in:  
* task ability  
* advisor beliefs  
  * benevolence  
  * ability  
  * integrity  
* general propensity to trust  
* general propensity to take advice  

The agents' general propensitites are correlated with one another, as are 
beliefs about advisors.  

```{r agentDefinition} 

makeAgents <- function(n) {
  agents <- tibble(
    id = 1:n,
    ability = rnorm(n),
    benevolence.a1 = rnorm(n),
    benevolence.a2 = rnorm(n),
    genTrust = rnorm(n)
  )
  
  for (a in c('a1', 'a2')) {
    for (vName in c('ability', 'integrity')) {
      b <- paste0('benevolence.', a)
      v <- paste0(vName, '.', a)
      agents[, v] <- rnorm(n) + 0.3 * agents[, b]
    }
  }
  
  agents$genTakeAdvice <- rnorm(n) + 0.3 * agents$genTrust
  
  agents
}

set.seed(10241024)
nAgents <- 100
nTrials <- 10

agents <- makeAgents(nAgents)

```

## Task performance

### Initial decision  

The agents perform tasks where they make an initial decision estimatie.
 Their performance is simply dependent on their ability (we note down the error)
.  
  
```{r initialDecision}

trials <- tibble(
  id = 1:(nAgents * nTrials),
  agentId = rep(agents$id, each = nTrials),
  initialDecision = rnorm(nAgents * nTrials, 
                          mean = rep(agents$ability, each = nTrials),
                          sd = rep(abs(agents$ability), each = nTrials))
)

```

### Advice and final decision  

Next agents get advice. They get advice from advisors. Advisors are either 
assigned to the same group or a different group. Groups are nominal, but change 
the perceived benevolence of advisors.   

```{r assignAdvisors}

agents$sameGroup.a1 <- runif(nAgents) > .5
agents$sameGroup.a2 <- !agents$sameGroup.a1

groupBonus <- 0.5

m <- agents$sameGroup.a1
agents$benevolence.a1[m] <- agents$benevolence.a1[m] + groupBonus
agents$benevolence.a2[!m] <- agents$benevolence.a2[!m] + groupBonus

```

Final decisions are based on the beliefs about the advisor and the general 
advice-taking propensity of the agent.  

```{r finalDecision}

trials$advisor <- ifelse(runif(nrow(trials)) < .5, 1, 2)
trials$advice <- runif(nrow(trials))

# throw some agents variables into trials for convenience
for (v in c('ability', 'benevolence', 'integrity')) {
  V <- paste0(v, ".a")
  trials[, V] <- NA
  trials[, V] <- unlist(sapply(1:nrow(trials), function(i) 
    agents[agents$id == trials$agentId[i], paste0(V, trials$advisor[i])]
    ))
}

trials$genTakeAdvice <- agents$genTakeAdvice[trials$agentId]

# final decision = initial decision + adviceTaking * advice
# adviceTaking = general + advisor beliefs

trials$finalDecision <- 
  trials$initialDecision + 
  (trials$genTakeAdvice + (trials$ability.a + 
                             trials$integrity.a + 
                             trials$benevolence.a) / 3) *
  trials$advice

```

## Analysis

