---
title: "Analysis script for DotTask"
output: 
  html_document:
  toc: true
  toc_float: true
  toc_collapsed: true
toc_depth: 3
number_sections: true
author: Matt Jaquiery (matt.jaquiery@psy.ox.ac.uk)
editor_options: 
  chunk_output_type: console
---
September 2018 

# 0) Support ####

## 0.i) Libraries ####
```{r echo = F, results = 'hide'}
if(!require(jsonlite)) {
  install.packages("jsonlite")
  library(jsonlite)
}
  
if(!require(BayesFactor)) {
  install.packages('BayesFactor')
  library(BayesFactor)
}

if(!require(tidyverse)) {
  install.packages('tidyverse')
  library(tidyverse)
}

if(!require(reshape2)) {
  install.packages('reshape2')
  library(reshape2)
}

if(!require(lme4)) {
  install.packages('lme4')
  library(lme4)
}

if(!require(lsr)) {
  install.packages('lsr')
  library(lsr)
}
if(!require(knitr)) {
  install.packages('knitr')
  library(knitr)
}
```

## 0.ii) Functions ####
```{r echo = F, results = 'hide'}
# Print the results of a t-test as we would like to see them reported in a paper
prettyPrint <- function(results, d = NULL) {
  es <- NULL
  if(!is.null(d))
    es <- paste0(' , d=', round(d,2))
  print(paste0('t(',results$parameter,')=',round(results$statistic,2),
               ' [',round(attr(results$conf.int, "conf.level")*100),'%CI: ',
               round(results$conf.int[[1]],2), ', ', round(results$conf.int[[2]],2),'],',
               ' p=',round(results$p.value,3), es))
}

# Print the mean and CIs of a vector
printMean <- function(vector, label = 'Mean', doPrint = T, conf.int = .95, na.rm = F, decimals = 2) {
  mu <- mean(vector, na.rm = na.rm)
  s <- sd(vector, na.rm = na.rm)
  n <- length(vector)
  error <- qnorm(1-(1-conf.int)/2)*s/sqrt(n) # 95% confidence interval width
  ci.low <- mu - error
  ci.high <- mu + error
  r <- round(range(vector, na.rm = na.rm), decimals)
  print(paste0(label,'=', round(mu,decimals), ' [', round(conf.int,decimals)*100, '%CI: ',
               round(ci.low,decimals), ', ', round(ci.high,decimals),'] [Range: ',
               r[[1]], ', ', r[[2]], ']'))
}

# Return the advice type of an advisor for participant with row number=pid
getAdviceTypeById <- function(aid, pid, advisor.data.frame) {
  type <- advisor.data.frame[which(advisor.data.frame$participantId==pid),]
  type <- type[which(type$id==aid),]
  if (length(type) > 0)
    return(type$adviceType)
  return(NA)
}
# Return a vector of advice types for trial list t
getAdviceType <- function (t, participant.data.frame, advisor.data.frame, forceRecalculate = FALSE) {
  # shortcut if we already calculated this
  if('adviceType' %in% colnames(t) && !forceRecalculate)
    return(t$adviceType)
  out <- vector(length=dim(t)[1])
  for (i in seq(length(out))) {
    if (t$advisorId[i]==0) {
      # no advisor
      out[i] <- NA;
    } else {
    pid <- t$participantId[i]
    out[i] <- getAdviceTypeById(t$advisorId[i], pid, advisor.data.frame)
    }
  }
  return(out)
}

#' Find the confidence shift in a given trial
#' @param t trial list
#' @param rawShift whether to report the confidence shift without adjusting for the assymetric scale
#' @param forceRecalulate if true, simply return the appropriate column from t if it exists already
#' @return a vector of confidence shifts for trial list t
getConfidenceShift <- function (t, rawShift = FALSE, forceRecalculate = FALSE) {
  scaleMaximum <- 50
  # shortcut if we already calculated this
  if('confidenceShift' %in% colnames(t) && !forceRecalculate)
    return(t$confidenceShift)
  out <- vector(length=dim(t)[1])
  for (i in seq(length(out))) {
    if (is.na(t$finalConfidence[i])) { # no advisor
      out[i] <- NA
    } else {
      max.shift <- scaleMaximum - t$initialConfidence[i]
      if(t$initialAnswer[i]==t$finalAnswer[i])
        out[i] <- t$finalConfidence[i]-t$initialConfidence[i] # same side
      else
        out[i] <- -1 * (t$finalConfidence[i]+t$initialConfidence[i]) # switched sliders, so went to 0 on the first one
      out[i] <- ifelse((abs(out[i]) > max.shift) & rawShift == F, max.shift*sign(out[i]), out[i])
    }
  }
  return(out)
}

# Return a vector of influence for trial list t
#' @param t trial list
#' @param rawShift whether to report the influence without adjusting for the assymetric scale
#' @param forceRecalulate if true, simply return the appropriate column from t if it exists already
#' @return a vector of influence for trial list t
getInfluence <- function (t, rawShift = FALSE, forceRecalculate = FALSE) {
  # shortcut if we already calculated this
  if('influence' %in% colnames(t) && !forceRecalculate)
    return(t$influence)
  out <- vector(length=dim(t)[1])
  for (i in seq(length(out))) {
    if (t$advisorId[i] == 0) { # no advisor
      out[i] <- NA
    } else {
      if (t$advisorAgrees[i])
        out[i] <- getConfidenceShift(t[i,], rawShift, forceRecalculate) # amount confidence increased
      else
        out[i] <- -1 * getConfidenceShift(t[i,], rawShift, forceRecalculate) # -1 * amount confidence increased
    }
  }
  return(out)
}

#' Get the name of the advice type
#' @param adviceType the advice type to fetch the name for
#' @param long whether to return the long name
#' @return string of the advice type, or NA by default
getAdviceTypeName <- function(adviceType, long = FALSE) {
  if(length(adviceType)>1) {
    out <- NULL
    for(aT in adviceType)
      out <- c(out, getAdviceTypeName(aT))
    return(out)
  }
  if(adviceType==adviceTypes$neutral)
    return(ifelse(long, 'neutral', 'Ntl'))
  if(adviceType==adviceTypes$AiC)
    return(ifelse(long,'Agree-in-confidence', 'AiC'))
  if(adviceType==adviceTypes$AiU)
    return(ifelse(long,'Agree-in-uncertainty', 'AiU'))
  if(adviceType==adviceTypes$HighAcc)
    return(ifelse(long,'High accuracy', 'HighAcc'))
  if(adviceType==adviceTypes$LowAcc)
    return(ifelse(long,'Low accuracy', 'LowAcc'))
  return(ifelse(long, 'None', NA))
}
```

## 0.iii) Globals ####
```{r echo = F, results = 'hide'}
# advice types: neutral, agree-in-confidence, and agree-in-uncertainty
adviceTypes <- list(neutral=0, AiC=3, AiU=4, HighAcc=5, LowAcc=6)
trialTypes <- list(catch=0, force=1, choice=2)
confidenceCategories <- list(low=0, medium=1, high=2)

# Advisor questionnaire dimensions
questionnaireDimensions <- list(accurate=1,
                                like=2,
                                trust=3,
                                influence=4)

# The Advisor portraits have properties which might affect ratings, so we should investigate these:
portraitDetails <- data.frame(
  portraitId = 1:5,
  category = factor(c('w', 'b', 'w', 'b', 'w')),
  blackProp = c(0, .99, 0, .99, .01),
  age = c(28.7, 24.9, 23.3, 24.6, 23.7)
)

# styling for ggplots
style <- theme_light() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major.x = element_blank(),
        legend.position = 'top')
style.long <- style + theme(legend.position = 'none')
```

# 1) Load data  ####
```{r echo = F, results='hide'}
print('Load data')
folderName <- '../DotTask/data/processed/'
files <- list.files(folderName)
participants <- NULL
trials <- NULL
advisors <- NULL
questionnaires <- NULL
genTrustQ <- NULL
for (i in seq(length(files))) {
  fileName <- paste(folderName, files[[i]], sep='/')
  json <- readChar(fileName, file.info(fileName)$size)
  jsonData <- fromJSON(json, simplifyVector = T, simplifyMatrix = T, simplifyDataFrame = T)
  # store all columns in participants table except the three last 
  # (trials, advisors, and questionnaires are stored separately)
  # Patch for missing data in practice
  participants <- rbind(participants, 
                        as.data.frame(t(jsonData[!names(jsonData) %in% c('advisors', 
                                                                         'questionnaires', 
                                                                         'trials',
                                                                         'generalisedTrustQuestionnaire')])))
  # store the trials in the trials table
  trials <- rbind(trials, jsonData$trials)
  if(('generalisedTrustQuestionnaire' %in% names(jsonData)))
    genTrustQ <- rbind(genTrustQ, jsonData$generalisedTrustQuestionnaire)
}
#rm(jsonData, files, fileName, folderName, json)
  
#   1.ii) Calculate utility variables ####
print('Calculate utility variables')
trials$initialCorrect <- trials$initialAnswer == trials$correctAnswer

# Convert times to seconds since the 70 epoch
participants$timeStart <- sapply(participants$timeStart, function(x)x[[1]]/1000)
participants$timeEnd <- sapply(participants$timeEnd, function(x)x[[1]]/1000)

# For convenience the long participant Id is shortened to a simple number:
participants$pid <- which(as.character(participants$id) == participants$id)
tmp <- function(x) participants$pid[which(participants$id == x)]
trials$pid <- sapply(trials$participantId, tmp)
genTrustQ$pid <- sapply(genTrustQ$participantId, tmp)

# The first general trust question is reverse coded
genTrustQ$answer <- as.numeric(genTrustQ$answer)
genTrustQ$answer[genTrustQ$order==0] <- 100 - genTrustQ$answer[genTrustQ$order==0]

#   1.iii) Split off real trials ####
print('Separate real trials from practice')
all.trials <- trials
trials <- trials[which(!trials$practice),]
```

# 2) Demographics ####
Demographic data are not collected and therefore not analysed


# 3) Manipulation checks ####
No manipulations occur so manipulation checks are not necessary.

# 4) Exclusions ####
Exclusion rules:

* Proportion of correct initial judgements must be (.60 < cor1/n < .90)
    * NB:practice trials are INCLUDED in this since they are used in part for determining confidence calibration
* Having fewer than 3 confidence categories
* Having fewer than 5% of trials in each confidence category
```{r echo = F, results = 'asis'}
participants$excluded <- sapply(participants$pid, function(pid){
  ts <- which(all.trials$pid == pid)
  # overall accuracy of initial decisions
  v <- all.trials$initialAnswer[ts] == all.trials$correctAnswer[ts]
  m <- mean(as.numeric(v), na.rm = T)
  if(m < .6 | m > .85)
    return('Accuracy')
  # varied use of confidence scale
  ts <- which(trials$pid == pid)
  cCs <- aggregate(pid ~ confidenceCategory, data = trials[ts, ], FUN = length)
  # All confidence categories must be used
  if(nrow(cCs) < 3)
    return ('Confidence')
  # Clarify the numbers on the rules below
  # All confidence categories must have at least 5% of the number of trials
  if(any(cCs$pid < length(ts)*.05))
    return('Confidence.cat')
  return(F)
  })
all.participants <- participants
participants <- participants[participants$excluded==F, ]
# Remove excluded participants' data from other data frames
trials <- trials[trials$pid %in% participants$pid, ]
advisors <- advisors[advisors$pid %in% participants$pid, ]
questionnaires <- questionnaires[questionnaires$pid %in% participants$pid, ]

df.iv <- aggregate(pid ~ excluded, data = all.participants, FUN = length)
names(df.iv) <- c('exclusionReason', 'count')
kable(df.iv)
```

# 5) Descriptives ####

## 5.i) Proportion correct ####
```{r echo = F, results = 'asis'}
x <- aggregate(initialCorrect ~ pid, trials, mean)$initialCorrect
cl <- mean_cl_normal(x)
rn <- range(x)
df.v.i <- data.frame(target = 71,
                     meanCorrect = cl$y, 
                     cl95Min = cl$ymin, cl95Max = cl$ymax,
                     rangeMin = rn[1], rangeMax = rn[2])
df.v.i <- round(df.v.i,3)
kable(df.v.i)
```

## 5.iii) Mean confidence ####

### 5.iii.i Mean confidence by correctness
```{r echo = F, results = 'asis'}
df.v.iii.i <- NULL
for(correct in list(T,F,c(T,F))) {
  x <- aggregate(initialConfidence ~ pid, trials[trials$initialCorrect %in% correct, ], mean)
  cl <- mean_cl_normal(x)
  rn <- range(x)
  df.v.iii.i <- rbind(df.v.iii.i, data.frame(correct = ifelse(length(correct)>1,'Both',correct), # hack to label total
                                             meanConfidence = cl$y,
                                             cl95Min = cl$ymin,
                                             cl95Max = cl$ymax,
                                             rangeMin = rn[1],
                                             rangeMax = rn[2]))
}
df.v.iii.i[,-1] <- round(df.v.iii.i[,-1],3)
kable(df.v.iii.i)
```

```{r eval = F}
# 15) Examining dot difference ####
ggplot(all.trials, aes(x = id, y = dotDifference, colour = as.factor(pid))) +
  geom_line() +
  geom_smooth(method = 'lm', se = F, data = all.trials[all.trials$block == max(all.trials$block), ]) +
  scale_x_continuous(limits = c(0,249)) +
  style.long +
  labs(title = 'Difficulty (and trend for the final block) for plain Dot Task')


# Cumulative accuracy plot
df.cumAcc <- NULL
limit <- 63
for(pid in unique(all.trials$pid)) {
  tmp <- all.trials[all.trials$pid == pid & all.trials$id > limit, ]
  for(id in unique(tmp$id)) {
    df.cumAcc <- rbind (df.cumAcc, data.frame(pid = as.factor(pid), 
                                              id,
                                              cumAcc = mean(tmp$initialCorrect[tmp$id<=id])))
  }
}
gg.cumAcc <- ggplot(df.cumAcc, aes(x = id, y = cumAcc, colour = pid)) +
  geom_line(alpha = 0.25) +
  stat_summary(geom = 'line', fun.y = mean, colour = 'red') +
  stat_summary(geom = 'ribbon', fun.data = mean_cl_normal, colour = NA, fill = 'red', alpha = 0.05) +
  annotate(geom = 'text', label = c('Mean', 'CL95% Low', 'CL95% High'),
           y = c(.175,.075,.025), x = 230, hjust = 1) +
  annotate(geom = 'text', 
           label = paste(round(mean_cl_normal(df.cumAcc$cumAcc[df.cumAcc$id==max(df.cumAcc$id)]),3)),
           y = c(.175,.075,.025), x = 240) +
  geom_hline(yintercept = .71, linetype = 'dashed', colour = 'black', size = 1) +
  scale_y_continuous(limits=c(0,1),breaks=seq(0,1,.05)) +
  style.long +
  labs(title = 'Cumulative accuracy plot for participants in the plain Dot Task')
gg.cumAcc

# 10-trial accuracy snapshots
df.accSnap <- NULL
for(i in seq(9,239,10)) {
  tmp <- aggregate(initialCorrect ~ pid, 
                   data = all.trials[all.trials$id > i, ],#%in% (i-4):(i+5), ], 
                   FUN = mean)
  tmp$i <- i
  df.accSnap <- rbind(df.accSnap, tmp)
}
ggplot(df.accSnap, aes(x=i, y=initialCorrect, colour=as.factor(pid))) + 
  geom_line(alpha = 0.25) +
  stat_summary(geom = 'line', fun.y = mean, colour = 'red') +
  stat_summary(geom = 'ribbon', fun.data = mean_cl_normal, colour = NA, fill = 'red', alpha = 0.05) +
  geom_hline(yintercept = .71, linetype = 'dashed', colour = 'black', size = 1)

```